---
title: "3_DiCA on balanced and unbalanced author's data"
author: "Ju-Chi.Yu"
date: "11/3/2021"
output: html_document
---

<style type="text/css">
.main-container {
max-width: 1800px;
margin-left: auto;
margin-right: auto;
}
</style>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(TInPosition)
library(PTCA4CATA)
library(ggplot2)
library(ggrepel)
library(tidyverse)
library(plotly)
library(RColorBrewer)
library(kableExtra)
library(ggpubr)
library(ggplotify)
# devtools:install_github("jokergoo/ComplexHeatmap")
# library(ComplexHeatmap)

load("../Data/EnFrAuthors_blnc_unblnc_cleaned.rda")

## get color ------------------
col.idx <- c("~Fr.18th" = "navy", "Fr.19th" = "royalblue2", "Fr.20th+" = "steelblue2", "~Eng.18th" = "brown", "~UK.18th" = "darkorange3", "UK.19th" = "darkorange2","UK.20th+" = "darkgoldenrod1", "~Amrc.19th" = "firebrick", "Amrc.20th+" = "palevioletred", "US.20th+" = "palevioletred")

col.group.blnc <- as.matrix(recode(data.dx.blncC$GroupDiCA, !!!col.idx))
rownames(col.group.blnc) <- data.dx.blncC$Authors

col.group.unblnc <- as.matrix(recode(data.dx.unblnc$GroupDiCA, !!!col.idx))
rownames(col.group.unblnc) <- data.dx.unblnc$Authors
```

# Data and results {.tabset}

This data set counts the number of punctuation from works of a selected list of authors. These authors are from US (1 from Canada), UK, and France and range from 14th to the 21st century. The idea of this analysis is to demonstrate that the use of punctuation can roughly represent style and can therefore differentiate authors of different style, background, and fields. Here, we include two analyses: one with balanced sample sizes (each group has the same number of authors), and the other with unbalanced sample sizes (the original selected set).

## Balanced data set

The balanced data set has 15 authors in these 7 groups:

|        |  ~18th  |  19th  |  20th+  |
|--------|:-------:|--------|---------|
| French |    15   |   15   |    15   |
|British |:   15  :|   15   |    15   |
|American|^^       |   -    |    15   |       


### The contingency table

```{r, include=FALSE}
knitr::kable(FrEnAuthors.blncC) %>% kable_styling("striped", full_width = F) %>% 
  scroll_box(width = "800px", height = "600px")
```

### The group pattern in heatmap
```{r, include=FALSE, fig.show = 'hold', out.width = "33.3%"}
coul <- colorRampPalette(brewer.pal(8, "PiYG"))(25) # Pink (Neg) to Green (Pos)

blnc.dx.disj <- makeNominalData(as.matrix(data.dx.blncC$GroupDiCA))
groupCntgy.blnc <- t(blnc.dx.disj) %*% FrEnAuthors.blncC
rownames(groupCntgy.blnc) <- sub(".","", rownames(groupCntgy.blnc))

# Original data
heatmap(groupCntgy.blnc, Rowv = NA, Colv = NA)
# Row profiles
heatmap(makeRowProfiles(groupCntgy.blnc)$rowProfiles, Rowv = NA, Colv = NA, )
# Deviation from independence
heatmap(makeRowProfiles(groupCntgy.blnc)$deviations, Rowv = NA, Colv = NA, col = coul)

```

### DiCA
```{r}
dica.blnc <- tepDICA.inference.battery(FrEnAuthors.blncC, make_data_nominal = FALSE, 
                                       blnc.dx.disj, make_design_nominal = FALSE, symmetric = TRUE, graphs = FALSE)
rownames(dica.blnc$Fixed.Data$TExPosition.Data$fi) <- sub(".","", rownames(dica.blnc$Fixed.Data$TExPosition.Data$fi))
colnames(dica.blnc$Fixed.Data$TExPosition.Data$fi) <- paste0("Component ", c(1:ncol(dica.blnc$Fixed.Data$TExPosition.Data$fi)))
colnames(dica.blnc$Fixed.Data$TExPosition.Data$fj) <- paste0("Component ", c(1:ncol(dica.blnc$Fixed.Data$TExPosition.Data$fj)))
colnames(dica.blnc$Fixed.Data$TExPosition.Data$fii) <- paste0("Component ", c(1:ncol(dica.blnc$Fixed.Data$TExPosition.Data$fii)))

PlotScree(dica.blnc$Fixed.Data$TExPosition.Data$eigs)
```

### Factor scores {.tabset}

#### Components 1 & 2

```{r, echo=FALSE, fig.show = 'hold', out.width = "50%"}
dica.blnc.fi <- dica.blnc$Fixed.Data$TExPosition.Data$fi
dica.blnc.fii <- dica.blnc$Fixed.Data$TExPosition.Data$fii
dica.blnc.fj <- dica.blnc$Fixed.Data$TExPosition.Data$fj

## Lables
dica.label12.blnc <- createxyLabels.gen(1,2,
                                        lambda = dica.blnc$Fixed.Data$TExPosition.Data$eigs,
                                        tau = round(dica.blnc$Fixed.Data$TExPosition.Data$t),
                                        axisName = "Component "
)

## Biplot
dica.fii12.blnc <- createFactorMap(dica.blnc.fii,
                                   axis1 = 1, axis2 = 2,
                                   constraints = minmaxHelper(dica.blnc.fii, dica.blnc.fj, axis1 = 1, axis2 = 2),
                                   col.points = col.group.blnc[rownames(dica.blnc.fii),], alpha.points = 0.2)
dica.plot12.blnc <- createFactorMapIJ(dica.blnc.fi, 
                                      dica.blnc.fj,axis1 = 1, axis2 = 2,
                                      text.cex.i = 4, cex.i = 4, pch.i = 17, alpha.points.i = 1,
                                      cex.j = 4, alpha.poin.j = 1,
                                      col.points.i = col.idx[rownames(dica.blnc.fi)],
                                      col.labels.i = col.idx[rownames(dica.blnc.fi)],
                                      title = "Authors by nationality x time")
dica.fii12.blnc$zeMap_background + dica.label12.blnc + dica.fii12.blnc$zeMap_dots + dica.plot12.blnc$I_points + dica.plot12.blnc$I_labels + dica.plot12.blnc$J_points + dica.plot12.blnc$J_labels

## Only Fj
dicaj.plot12.blnc <- createFactorMap(dica.blnc.fj,
                                     axis1 = 1, axis2 = 2, 
                                     text.cex = 5,
                                     col.points = "darkolivegreen",
                                     col.labels = "darkolivegreen",
                                     pch = 18,
                                     title = "Punctuations - balanced")#,

dicaj.plot12.blnc$zeMap + dica.label12.blnc
```

```{r, echo=FALSE}
## Only Fii
fii2plot <- dica.blnc.fii[,1:2] %>% as.data.frame
fj2plot <- dica.blnc.fj[,1:2] %>% as.data.frame
colnames(fj2plot) <- colnames(fii2plot) <- paste0("Component", c(1,2))

p2 <- ggplot() +
  geom_hline(yintercept = 0, size = 0.1) + geom_vline(xintercept = 0, size = 0.1) +
  geom_point(data = fii2plot, aes(x = Component1, y = Component2, 
                                 text = rownames(dica.blnc.fii)), 
             color = col.group.blnc[rownames(dica.blnc.fii),]) +
  geom_point(data = fj2plot, aes(x = Component1, y = Component2), color = "darkolivegreen", pch = 18, size = 3) + 
  geom_text(data = fj2plot, aes(x = Component1, y = Component2, label = rownames(dica.blnc.fj)), color = "darkolivegreen", size = 5, nudge_y = 0.08) + 
  coord_equal() +
  theme_bw()

ggplotly(p2, tooltip = c("text"))
```


#### Components 3 and 4

```{r, echo=FALSE, fig.show = 'hold', out.width = "33.33%"}
## Lables
dica.label34.blnc <- createxyLabels.gen(3,4,
                                      lambda = dica.blnc$Fixed.Data$TExPosition.Data$eigs,
                                      tau = round(dica.blnc$Fixed.Data$TExPosition.Data$t),
                                      axisName = "Component "
)

## Biplot
dica.fii34.blnc <- createFactorMap(dica.blnc.fii,
                                   axis1 = 3, axis2 = 4,
                                   constraints = minmaxHelper(dica.blnc.fii, dica.blnc.fj, axis1 = 3, axis2 = 4),
                                   col.points = col.group.blnc[rownames(dica.blnc.fii),], alpha.points = 0.2)
dica.plot34.blnc <- createFactorMapIJ(dica.blnc.fi, 
                                      dica.blnc.fj,axis1 = 3, axis2 = 4,
                                      text.cex.i = 4, cex.i = 4, pch.i = 17, alpha.points.i = 1,
                                      cex.j = 4, alpha.poin.j = 1,
                                      col.points.i = col.idx[rownames(dica.blnc.fi)],
                                      col.labels.i = col.idx[rownames(dica.blnc.fi)],
                                      title = "Authors by nationality x time")
dica.fii34.blnc$zeMap_background + dica.label34.blnc + dica.fii34.blnc$zeMap_dots + dica.plot34.blnc$I_points + dica.plot34.blnc$I_labels

dica.plot34.blnc$baseMap + dica.label34.blnc + dica.fii34.blnc$zeMap_dots + dica.plot34.blnc$I_points + dica.plot34.blnc$I_labels + dica.plot34.blnc$J_points + dica.plot34.blnc$J_labels

## Only Fj
dicaj.plot34.blnc <- createFactorMap(dica.blnc.fj,
                                   axis1 = 3, axis2 = 4, 
                                   text.cex = 5,
                                   col.points = "darkolivegreen",
                                   col.labels = "darkolivegreen",
                                   pch = 18,
                                   title = "Punctuations - balanced")#,

dicaj.plot34.blnc$zeMap + dica.label34.blnc
```

```{r, echo=FALSE}
## Only Fii
fii2plot <- dica.blnc.fii[,3:4] %>% as.data.frame
fj2plot <- dica.blnc.fj[,3:4] %>% as.data.frame
colnames(fj2plot) <- colnames(fii2plot) <- paste0("Component", c(3,4))

p2 <- ggplot() +
  geom_hline(yintercept = 0, size = 0.1) + geom_vline(xintercept = 0, size = 0.1) +
  geom_point(data = fii2plot, aes(x = Component3, y = Component4, 
                                 text = rownames(dica.blnc.fii)), 
             color = col.group.blnc[rownames(dica.blnc.fii),]) +
  geom_point(data = fj2plot, aes(x = Component3, y = Component4), color = "darkolivegreen", pch = 18, size = 3) + 
  geom_text(data = fj2plot, aes(x = Component3, y = Component4, label = rownames(dica.blnc.fj)), color = "darkolivegreen", size = 5, nudge_y = 0.08) + 
  coord_equal() +
  theme_bw()

ggplotly(p2, tooltip = c("text"))

```


### Factor scores with confidence intervals {.tabset}

#### Components 1 & 2

```{r, echo=FALSE, fig.show = 'hold', out.width = "50%"}
dica.blnc.boot <- dica.blnc$Inference.Data$boot.data$fi.boot.data$boots
rownames(dica.blnc.boot) <- sub(".", "", rownames(dica.blnc.boot))
colnames(dica.blnc.boot) <- paste0("Component ", c(1:ncol(dica.blnc.boot)))

dicaCI.12.blnc <- MakeCIEllipses(dica.blnc.boot, axis1 = 1, axis2 = 2, 
                                   names.of.factors = paste0("Component ", c(1:2)),
                                   col = col.idx[rownames(dica.blnc.boot)], 
                                   p.level = .95, line.size = 0.5, alpha.line = 0.5, alpha.ellipse = 0.1)
dicaTI.12.blnc <- MakeToleranceIntervals(dica.blnc.fii,
                                       data.dx.blncC$GroupDiCA,
                                       axis1 = 1, axis2 = 2,
                                       names.of.factors = paste0("Component ", c(1:2)),
                                       col = col.idx[levels(data.dx.blncC$GroupDiCA)],
                                       p.level = .95, 
                                       line.size = 0.5, alpha.line = 0.5, alpha.ellipse = 0.05)

dica.plot12.blnc$baseMap + dicaCI.12.blnc + dica.plot12.blnc$I_labels + dica.plot12.blnc$I_points + dica.plot12.blnc$J_labels + dica.plot12.blnc$J_points + dica.label12.blnc

dica.fii12.blnc$zeMap_background + dicaTI.12.blnc + dica.plot12.blnc$I_labels + dica.plot12.blnc$I_points + dica.plot12.blnc$J_labels + dica.plot12.blnc$J_points + dica.label12.blnc

```

#### Components 3 & 4

```{r, echo=FALSE, fig.show = 'hold', out.width = "50%"}
dicaCI.34.blnc <- MakeCIEllipses(dica.blnc.boot, axis1 = 3, axis2 = 4, 
                                   names.of.factors = paste0("Component ", c(3:4)),
                                   col = col.idx[rownames(dica.blnc.boot)], 
                                   p.level = .95, line.size = 0.5, alpha.line = 0.5, alpha.ellipse = 0.1)
dicaTI.34.blnc <- MakeToleranceIntervals(dica.blnc.fii,
                                       data.dx.blncC$GroupDiCA,
                                       axis1 = 3, axis2 = 4,
                                       names.of.factors = paste0("Component ", c(3:4)),
                                       col = col.idx[levels(data.dx.blncC$GroupDiCA)],
                                       p.level = .95, 
                                       line.size = 0.5, alpha.line = 0.5, alpha.ellipse = 0.05)

dica.fii34.blnc$zeMap_background + dicaCI.34.blnc + dica.plot34.blnc$I_labels + dica.plot34.blnc$I_points + dica.plot34.blnc$J_labels + dica.plot34.blnc$J_points + dica.label34.blnc

dica.fii34.blnc$zeMap_background + dicaTI.34.blnc + dica.plot34.blnc$I_labels + dica.plot34.blnc$I_points + dica.plot34.blnc$J_labels + dica.plot34.blnc$J_points + dica.label34.blnc

```

## Unbalanced data set

The unbalanced data set includes 160 authors of these 8 groups:

|        |  ~18th  |  19th  |  20th+  |
|--------|:-------:|:------:|---------|
| French |    16   |   28   |    19   |
|British |    11   |   28   |    22   |
|American|    14           ||    22   |       


### The contingency table

```{r, echo=FALSE}
knitr::kable(FrEnAuthors.unblnc) %>% kable_styling("striped", full_width = F) %>% 
  scroll_box(width = "800px", height = "600px")
```

### The group pattern in heatmap
```{r, include=FALSE, fig.show = 'hold', out.width = "33.3%"}
unblnc.dx.disj <- makeNominalData(as.matrix(data.dx.unblnc$GroupDiCA))
groupCntgy.unblnc <- t(unblnc.dx.disj) %*% FrEnAuthors.unblnc
rownames(groupCntgy.unblnc) <- sub(".","", rownames(groupCntgy.unblnc))

# Original data
heatmap(groupCntgy.unblnc, Rowv = NA, Colv = NA)
# Row profiles
heatmap(makeRowProfiles(groupCntgy.unblnc)$rowProfiles, Rowv = NA, Colv = NA, )
# Deviation from independence
heatmap(makeRowProfiles(groupCntgy.unblnc)$deviations, Rowv = NA, Colv = NA, col = coul)

```

### DiCA
```{r}
dica.unblnc <- tepDICA.inference.battery(FrEnAuthors.unblnc, make_data_nominal = FALSE, 
                                       unblnc.dx.disj, make_design_nominal = FALSE, symmetric = TRUE, graphs = FALSE)
rownames(dica.unblnc$Fixed.Data$TExPosition.Data$fi) <- sub(".","", rownames(dica.unblnc$Fixed.Data$TExPosition.Data$fi))
colnames(dica.unblnc$Fixed.Data$TExPosition.Data$fi) <- paste0("Component ", c(1:ncol(dica.unblnc$Fixed.Data$TExPosition.Data$fi)))
colnames(dica.unblnc$Fixed.Data$TExPosition.Data$fj) <- paste0("Component ", c(1:ncol(dica.unblnc$Fixed.Data$TExPosition.Data$fj)))
colnames(dica.unblnc$Fixed.Data$TExPosition.Data$fii) <- paste0("Component ", c(1:ncol(dica.unblnc$Fixed.Data$TExPosition.Data$fii)))

PlotScree(dica.unblnc$Fixed.Data$TExPosition.Data$eigs)
```

### Factor scores {.tabset}

#### Components 1 & 2

```{r, echo=FALSE, fig.show = 'hold', out.width = "50%"}
dica.unblnc.fi <- dica.unblnc$Fixed.Data$TExPosition.Data$fi
dica.unblnc.fii <- dica.unblnc$Fixed.Data$TExPosition.Data$fii
dica.unblnc.fj <- dica.unblnc$Fixed.Data$TExPosition.Data$fj

## Lables
dica.label12.unblnc <- createxyLabels.gen(1,2,
                                        lambda = dica.unblnc$Fixed.Data$TExPosition.Data$eigs,
                                        tau = round(dica.unblnc$Fixed.Data$TExPosition.Data$t),
                                        axisName = "Component "
)

## Biplot
dica.fii12.unblnc <- createFactorMap(dica.unblnc.fii,
                                   axis1 = 1, axis2 = 2,
                                   constraints = minmaxHelper(dica.unblnc.fii, dica.unblnc.fj, axis1 = 1, axis2 = 2),
                                   col.points = col.group.unblnc[rownames(dica.unblnc.fii),], alpha.points = 0.2)
dica.plot12.unblnc <- createFactorMapIJ(dica.unblnc.fi, 
                                      dica.unblnc.fj,axis1 = 1, axis2 = 2,
                                      text.cex.i = 4, cex.i = 4, pch.i = 17, alpha.points.i = 1,
                                      cex.j = 4, alpha.poin.j = 1,
                                      col.points.i = col.idx[rownames(dica.unblnc.fi)],
                                      col.labels.i = col.idx[rownames(dica.unblnc.fi)],
                                      title = "Authors by nationality x time")
dica.fii12.unblnc$zeMap_background + dica.label12.unblnc + dica.fii12.unblnc$zeMap_dots + dica.plot12.unblnc$I_points + dica.plot12.unblnc$I_labels + dica.plot12.unblnc$J_points + dica.plot12.unblnc$J_labels

## Only Fj
dicaj.plot12.unblnc <- createFactorMap(dica.unblnc.fj,
                                     axis1 = 1, axis2 = 2, 
                                     text.cex = 5,
                                     col.points = "darkolivegreen",
                                     col.labels = "darkolivegreen",
                                     pch = 18,
                                     title = "Punctuations - balanced")#,

dicaj.plot12.unblnc$zeMap + dica.label12.unblnc
```

```{r, echo=FALSE}
## Only Fii
fii2plot <- dica.unblnc.fii[,1:2] %>% as.data.frame
fj2plot <- dica.unblnc.fj[,1:2] %>% as.data.frame
colnames(fj2plot) <- colnames(fii2plot) <- paste0("Component", c(1,2))

p2 <- ggplot() +
  geom_hline(yintercept = 0, size = 0.1) + geom_vline(xintercept = 0, size = 0.1) +
  geom_point(data = fii2plot, aes(x = Component1, y = Component2, 
                                 text = rownames(dica.unblnc.fii)), 
             color = col.group.unblnc[rownames(dica.unblnc.fii),]) +
  geom_point(data = fj2plot, aes(x = Component1, y = Component2), color = "darkolivegreen", pch = 18, size = 3) + 
  geom_text(data = fj2plot, aes(x = Component1, y = Component2, label = rownames(dica.unblnc.fj)), color = "darkolivegreen", size = 5, nudge_y = 0.08) + 
  coord_equal() +
  theme_bw()

ggplotly(p2, tooltip = c("text"))
```


#### Components 3 and 4

```{r, echo=FALSE, fig.show = 'hold', out.width = "33.33%"}
## Lables
dica.label34.unblnc <- createxyLabels.gen(3,4,
                                      lambda = dica.unblnc$Fixed.Data$TExPosition.Data$eigs,
                                      tau = round(dica.unblnc$Fixed.Data$TExPosition.Data$t),
                                      axisName = "Component "
)

## Biplot
dica.fii34.unblnc <- createFactorMap(dica.unblnc.fii,
                                   axis1 = 3, axis2 = 4,
                                   constraints = minmaxHelper(dica.unblnc.fii, dica.unblnc.fj, axis1 = 3, axis2 = 4),
                                   col.points = col.group.unblnc[rownames(dica.unblnc.fii),], alpha.points = 0.2)
dica.plot34.unblnc <- createFactorMapIJ(dica.unblnc.fi, 
                                      dica.unblnc.fj,axis1 = 3, axis2 = 4,
                                      text.cex.i = 4, cex.i = 4, pch.i = 17, alpha.points.i = 1,
                                      cex.j = 4, alpha.poin.j = 1,
                                      col.points.i = col.idx[rownames(dica.unblnc.fi)],
                                      col.labels.i = col.idx[rownames(dica.unblnc.fi)],
                                      title = "Authors by nationality x time")
dica.fii34.unblnc$zeMap_background + dica.label34.unblnc + dica.fii34.unblnc$zeMap_dots + dica.plot34.unblnc$I_points + dica.plot34.unblnc$I_labels

dica.plot34.unblnc$baseMap + dica.label34.unblnc + dica.fii34.unblnc$zeMap_dots + dica.plot34.unblnc$I_points + dica.plot34.unblnc$I_labels + dica.plot34.unblnc$J_points + dica.plot34.unblnc$J_labels

## Only Fj
dicaj.plot34.unblnc <- createFactorMap(dica.unblnc.fj,
                                   axis1 = 3, axis2 = 4, 
                                   text.cex = 5,
                                   col.points = "darkolivegreen",
                                   col.labels = "darkolivegreen",
                                   pch = 18,
                                   title = "Punctuations - balanced")#,

dicaj.plot34.unblnc$zeMap + dica.label34.unblnc
```

```{r, echo=FALSE}
## Only Fii
fii2plot <- dica.unblnc.fii[,3:4] %>% as.data.frame
fj2plot <- dica.unblnc.fj[,3:4] %>% as.data.frame
colnames(fj2plot) <- colnames(fii2plot) <- paste0("Component", c(3,4))

p2 <- ggplot() +
  geom_hline(yintercept = 0, size = 0.1) + geom_vline(xintercept = 0, size = 0.1) +
  geom_point(data = fii2plot, aes(x = Component3, y = Component4, 
                                 text = rownames(dica.unblnc.fii)), 
             color = col.group.unblnc[rownames(dica.unblnc.fii),]) +
  geom_point(data = fj2plot, aes(x = Component3, y = Component4), color = "darkolivegreen", pch = 18, size = 3) + 
  geom_text(data = fj2plot, aes(x = Component3, y = Component4, label = rownames(dica.unblnc.fj)), color = "darkolivegreen", size = 5, nudge_y = 0.08) + 
  coord_equal() +
  theme_bw()

ggplotly(p2, tooltip = c("text"))

```


### Factor scores with confidence intervals {.tabset}

#### Components 1 & 2

```{r, echo=FALSE, fig.show = 'hold', out.width = "50%"}
dica.unblnc.boot <- dica.unblnc$Inference.Data$boot.data$fi.boot.data$boots
rownames(dica.unblnc.boot) <- sub(".", "", rownames(dica.unblnc.boot))
colnames(dica.unblnc.boot) <- paste0("Component ", c(1:ncol(dica.unblnc.boot)))

dicaCI.12.unblnc <- MakeCIEllipses(dica.unblnc.boot, axis1 = 1, axis2 = 2, 
                                   names.of.factors = paste0("Component ", c(1:2)),
                                   col = col.idx[rownames(dica.unblnc.boot)], 
                                   p.level = .95, line.size = 0.5, alpha.line = 0.5, alpha.ellipse = 0.1)
dicaTI.12.unblnc <- MakeToleranceIntervals(dica.unblnc.fii,
                                       data.dx.unblnc$GroupDiCA,
                                       axis1 = 1, axis2 = 2,
                                       names.of.factors = paste0("Component ", c(1:2)),
                                       col = col.idx[levels(data.dx.unblnc$GroupDiCA)],
                                       p.level = .95, 
                                       line.size = 0.5, alpha.line = 0.5, alpha.ellipse = 0.05)

dica.plot12.unblnc$baseMap + dicaCI.12.unblnc + dica.plot12.unblnc$I_labels + dica.plot12.unblnc$I_points + dica.plot12.unblnc$J_labels + dica.plot12.unblnc$J_points + dica.label12.unblnc

dica.fii12.unblnc$zeMap_background + dicaTI.12.unblnc + dica.plot12.unblnc$I_labels + dica.plot12.unblnc$I_points + dica.plot12.unblnc$J_labels + dica.plot12.unblnc$J_points + dica.label12.unblnc

```

#### Components 3 & 4

```{r, echo=FALSE, fig.show = 'hold', out.width = "50%"}
dicaCI.34.unblnc <- MakeCIEllipses(dica.unblnc.boot, axis1 = 3, axis2 = 4, 
                                   names.of.factors = paste0("Component ", c(3:4)),
                                   col = col.idx[rownames(dica.unblnc.boot)], 
                                   p.level = .95, line.size = 0.5, alpha.line = 0.5, alpha.ellipse = 0.1)
dicaTI.34.unblnc <- MakeToleranceIntervals(dica.unblnc.fii,
                                       data.dx.unblnc$GroupDiCA,
                                       axis1 = 3, axis2 = 4,
                                       names.of.factors = paste0("Component ", c(3:4)),
                                       col = col.idx[levels(data.dx.unblnc$GroupDiCA)],
                                       p.level = .95, 
                                       line.size = 0.5, alpha.line = 0.5, alpha.ellipse = 0.05)

dica.fii34.unblnc$zeMap_background + dicaCI.34.unblnc + dica.plot34.unblnc$I_labels + dica.plot34.unblnc$I_points + dica.plot34.unblnc$J_labels + dica.plot34.unblnc$J_points + dica.label34.unblnc

dica.fii34.unblnc$zeMap_background + dicaTI.34.unblnc + dica.plot34.unblnc$I_labels + dica.plot34.unblnc$I_points + dica.plot34.unblnc$J_labels + dica.plot34.unblnc$J_points + dica.label34.unblnc

```